---
title: "d15N CSIA Analysis"
author: "Caila Kucheravy"
---

Load packages and prep environment: 
```{r, echo = TRUE, message = FALSE, results = 'hide', warning = FALSE}
# Clear environment:
# rm(list=ls())

# Set working directory to source file location

# Load packages
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
library(stats)
library(lubridate)
library(ggfortify)
library(brms)
library(bayesplot)
library(tidybayes)
library(cowplot)
library(factoextra)
library(ggrepel)
```

## Load and format data:

Load d15N amino acid data & prep for analysis: 
```{r}
# Load data including means and standard error 
d15N_AA <- read.csv("d15N_AA.csv", header = TRUE)

# Prep data:
d15N_means <- d15N_AA %>% 
  # Filter for means
  filter(mean_se == "mean") %>% 
  # Create new column for sampling group (group sampled in a given year and location)
  unite(Group, c("Location", "Year"), sep = " ", remove = FALSE) %>% 
  # Add columns for trophic AAs (Glx and Thr) corrected to Phe:
  mutate(Glx_Phe = Glx - Phe,
         Thr_Phe = Thr - Phe) 

# Convert calendar date to julian day:
d15N_means$Sample_date <- as.Date(d15N_means$Sample_date, "%Y-%m-%d")

d15N_means <- d15N_means %>% 
  mutate(julian_day = yday(d15N_means$Sample_date)) %>% 
  relocate(julian_day, .after = Sample_date)

# In the data there are same year and across-year duplicates - note that some samples have both within year and across year duplicates
# Same year duplicate coding: 
# 0 = no duplicate 
# 1 = duplicate sample, first collected 
# 2 = duplicate sample, second collected (excluded in analysis)

# Across year duplicate coding: 
# 0 = no duplicate 
# 1 = duplicate sample, first collected (earlier year)
# 2 = duplicate sample, second collected (sometimes same year as 1 if there is a 3, sometimes different year than 1)
# 3 = duplicate sample, third collected (sometimes same year as 2, sometimes different year than 1 & 2)

# Filter out same year and across year duplicates 
d15N_dups_removed <- d15N_means %>% 
  filter(!duplicate_in_year == "2") %>% 
  filter(!duplicate_other_year > 1)
```

Save data frame: 
```{r}
# write_rds(d15N_dups_removed, "d15N_dups_removed.rds")
```

## Genetic populations

Population-specific mean ± SE:
```{r}
# Glx - Phe
d15N_dups_removed %>% 
    group_by(genetic_pop) %>%
    dplyr::summarize(Mean = mean(Glx_Phe),
                     SE = plotrix::std.error(Glx_Phe))
# Thr
d15N_dups_removed %>% 
    group_by(genetic_pop) %>%
    dplyr::summarize(Mean = mean(Thr),
                     SE = plotrix::std.error(Thr))
# Thr - Phe
d15N_dups_removed %>% 
    group_by(genetic_pop) %>%
    dplyr::summarize(Mean = mean(Thr_Phe),
                     SE = plotrix::std.error(Thr_Phe))

# Phe
d15N_dups_removed %>% 
    group_by(genetic_pop) %>%
    dplyr::summarize(Mean = mean(Phe),
                     SE = plotrix::std.error(Phe))

# Lys
d15N_dups_removed %>% 
    group_by(genetic_pop) %>%
    dplyr::summarize(Mean = mean(Lys),
                     SE = plotrix::std.error(Lys))
```

Re-arrange data for violin plots: 
```{r}
# Trophic AAs: glx, asx, ala, ile, leu, pro, val, thr
# Source AAs: phe, lys

# Rearrange the data for plotting 
d15N_means_rearrange <- d15N_dups_removed %>% 
  dplyr::select(all_of(c("Group", "Location", "Year", "DFO_sample_id", "csia_sample_id", "genetic_pop", "sex", "Phe", "Lys", "Glx_Phe", "Thr", "Thr_Phe"))) %>% 
  pivot_longer(8:12)

# Order AAs for plotting
d15N_means_rearrange$name <- factor(d15N_means_rearrange$name, levels = c("Phe", "Lys", "Glx_Phe", "Thr", "Thr_Phe"))
```

Boxplots by genetic population: 
```{r}
outline_cols <- c("#0072B2", "#E69F00")
fill_cols <- c("#c6eaff", "#fff1d2")

# Arrange data for Phe, Lys, and Glx-Phe
d15N_means_rearrange_most <- d15N_means_rearrange %>% 
  dplyr::filter(!name %in% c("Thr", "Thr_Phe")) 

# Arrange data for Thr and Thr-Phe
d15N_means_rearrange_thr <- d15N_means_rearrange %>% 
  dplyr::filter(name %in% c("Thr", "Thr_Phe")) 

# Plot Phe, Lys, and Glx-Phe
most <- ggplot(data = d15N_means_rearrange_most, aes(x = name, y = value, fill = genetic_pop, colour = genetic_pop)) + 
  geom_rect(aes(xmin = 0.5, xmax = 2.5, ymin = -Inf, ymax = Inf), fill = "grey93", colour = NA) +
  geom_violin(position = position_dodge(0.75)) + 
  geom_boxplot(width = 0.075, position = position_dodge(0.75), fill = "white") +
  geom_point(position = position_jitterdodge(jitter.width = 0.2), size = 0.3, alpha = 0.6) +
  ylim(0,35) +
  ylab(expression(paste(delta^{15}, "N", " (\u2030)"))) +
  scale_fill_manual(values = fill_cols) + 
  scale_colour_manual(values = outline_cols) +
  scale_x_discrete(labels = c("Phe" = "Phe", "Lys" = "Lys", "Glx_Phe" = "Glx-Phe")) +
  theme_classic() + 
  theme(legend.position = "none",
        legend.background = element_blank(),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        axis.title.x = element_blank())

# Plot Thr and Thr-Phe
thr <- ggplot(data = d15N_means_rearrange_thr, aes(x = name, y = value, fill = genetic_pop, colour = genetic_pop)) + 
  geom_violin(position = position_dodge(0.75)) + 
  geom_boxplot(width = 0.075, position = position_dodge(0.75), fill = "white") +
  geom_point(position = position_jitterdodge(jitter.width = 0.2), size = 0.3, alpha = 0.6) +
  ylim(-70,-35) +
  scale_fill_manual(values = fill_cols) + 
  scale_colour_manual(values = outline_cols) +
  scale_x_discrete(labels = c("Thr" = "Thr", "Thr_Phe" = "Thr-Phe")) +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 14))

# Combine plots
plot_grid(most, thr, rel_widths = c(1.5,1), labels = NA)

# ggsave("manuscript_plots/violinplots_d15N_allAAs.jpg", dpi = 300, width = 10, height = 5)
```

Test if Glx-Phe, Thr, Thr-Phe, Phe, and Lys differs between genetic populations. Using brms default priors that are non or weakly informative (negligible effect). See diagnostics and posterior predictive checks, etc. for brms models at the end.

Glx - Phe:
```{r}
# # Model (run on server)
# Glx_Phe__genetic_pop <- brm(Glx_Phe ~ genetic_pop,
#                               data = d15N_dups_removed,
#                               warmup = 20000,
#                               iter = 50000,
#                               chains = 3,
#                               init = "random",
#                               cores = 2)
# 
# # Save model (server):
# saveRDS(Glx_Phe__genetic_pop, "output/Glx_Phe__genetic_pop.rds")

# Load model and view results
Glx_Phe__genetic_pop <- readRDS("server/Glx_Phe__genetic_pop.rds")
summary(Glx_Phe__genetic_pop) # Differs between pops
```

Thr: 
```{r}
# # Model (run on server)
# Thr__genetic_pop <- brm(Thr ~ genetic_pop,
#                               data = d15N_dups_removed,
#                               warmup = 20000,
#                               iter = 50000,
#                               chains = 3,
#                               init = "random",
#                               cores = 2)
# 
# # Save model (server):
# saveRDS(Thr__genetic_pop, "output/Thr__genetic_pop.rds")

# Load model and view results
Thr__genetic_pop <- readRDS("server/Thr__genetic_pop.rds")
summary(Thr__genetic_pop) # Differs between pops
```

Thr-Phe: 
```{r}
# #Model (run on server)
# Thr_Phe__genetic_pop <- brm(Thr_Phe ~ genetic_pop,
#                               data = d15N_dups_removed,
#                               warmup = 20000,
#                               iter = 50000,
#                               chains = 3,
#                               init = "random",
#                               cores = 2)
# 
# # Save model (server):
# saveRDS(Thr_Phe__genetic_pop, "output/Thr_Phe__genetic_pop.rds")

# Load model and view results
Thr_Phe__genetic_pop <- readRDS("server/Thr_Phe__genetic_pop.rds")
summary(Thr_Phe__genetic_pop) # Differs between pops
```

Phe:
```{r}
# # Model (run on server)
# Phe__genetic_pop <- brm(Phe ~ genetic_pop,
#                           data = d15N_dups_removed,
#                           warmup = 20000,
#                           iter = 50000,
#                           chains = 3,
#                           init = "random",
#                           cores = 2)
# 
# # Save model (server):
# saveRDS(Phe__genetic_pop, "output/Phe__genetic_pop.rds")

# Load model and view results
Phe__genetic_pop <- readRDS("server/Phe__genetic_pop.rds")
summary(Phe__genetic_pop) # No difference
```

Lys:
```{r}
# # Model (run on server)
# Lys__genetic_pop <- brm(Lys ~ genetic_pop,
#                           data = d15N_dups_removed,
#                           warmup = 20000,
#                           iter = 50000,
#                           chains = 3,
#                           init = "random",
#                           cores = 2)
# 
# # Save model (server):
# saveRDS(Lys__genetic_pop, "output/Lys__genetic_pop.rds")

# Load model and view results
Lys__genetic_pop <- readRDS("server/Lys__genetic_pop.rds")
summary(Lys__genetic_pop) # No difference
```

## Genetic subpopulations

Add column for genetic subpopulations to data frame: 
```{r}
# Attach subpop classification to d15 dataset
d15N_dups_removed_subpops <- d15N_dups_removed %>% 
  dplyr::mutate(genetic_subpop = ifelse(genetic_pop == "ECAG2", "ECAG2",
                                        ifelse(Location %in% c("St. P & M", "Newfoundland"), "ECAG1_South", "ECAG1_North"))) %>% 
  relocate(genetic_subpop, .after = genetic_pop)
```

Re-arrange data for plotting: 
```{r}
d15N_subpops_rearrange <- d15N_dups_removed_subpops %>% 
  dplyr::select(all_of(c("Group", "Location", "Year", "DFO_sample_id", "csia_sample_id", "genetic_pop", "genetic_subpop", "sex", "Glx_Phe", "Thr", "Thr_Phe"))) %>% 
  pivot_longer(9:11)

# Order AAs for plotting
d15N_subpops_rearrange$name <- factor(d15N_subpops_rearrange$name, levels = c("Glx_Phe", "Thr", "Thr_Phe"))

# Arrange data for Phe, Lys, and Glx-Phe
d15N_subpops_rearrange_glx <- d15N_subpops_rearrange %>% 
  dplyr::filter(name %in% c("Glx_Phe")) 

# Arrange data for Thr and Thr-Phe
d15N_subpops_rearrange_thr <- d15N_subpops_rearrange %>% 
  dplyr::filter(name %in% c("Thr", "Thr_Phe")) 
```

Violin plots:
```{r}
# Set subpopulation colors 
subpop_outline_cols <- c("#0072B2", "#009e73", "#E69F00")
subpop_fill_cols    <- c("#c6eaff", "#c5ffef", "#fff1d2")

# Plot Phe, Lys, and Glx-Phe
glx_subpops <- ggplot(data = d15N_subpops_rearrange_glx, aes(x = name, y = value, fill = genetic_subpop, colour = genetic_subpop)) + 
  geom_violin(position = position_dodge(0.75)) + 
  geom_boxplot(width = 0.075, position = position_dodge(0.75), fill = "white") +
  geom_point(position = position_jitterdodge(jitter.width = 0.1), size = 0.3, alpha = 0.6) +
  ylim(0,40) +
  ylab(expression(paste(delta^{15}, "N", " (\u2030)"))) +
  scale_fill_manual(values = subpop_fill_cols) + 
  scale_colour_manual(values = subpop_outline_cols) +
  scale_x_discrete(labels = c("Glx_Phe" = "Glx-Phe")) +
  theme_classic() + 
  theme(legend.position = "none",
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        axis.title.x = element_blank())

# Plot Thr and Thr-Phe
thr_subpops <- ggplot(data = d15N_subpops_rearrange_thr, aes(x = name, y = value, fill = genetic_subpop, colour = genetic_subpop)) + 
  geom_violin(position = position_dodge(0.75)) + 
  geom_boxplot(width = 0.075, position = position_dodge(0.75), fill = "white") +
  geom_point(position = position_jitterdodge(jitter.width = 0.1), size = 0.3, alpha = 0.6) +
  ylim(-70,-30) +
  scale_fill_manual(values = subpop_fill_cols, name = "Genetic Subpop", labels = c("ECAG1 North", "ECAG1 South", "ECAG2")) + 
  scale_colour_manual(values = subpop_outline_cols, name = "Genetic Subpop", labels = c("ECAG1 North", "ECAG1 South", "ECAG2")) +
  scale_x_discrete(labels = c("Thr" = "Thr", "Thr_Phe" = "Thr-Phe")) +
  theme_classic() +
  theme(legend.position = "none",
        # legend.position = c(0.75, 0.8),
        # legend.text = element_text(size = 14),
        # legend.title = element_text(size = 16),
        legend.background = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 14))

# Combine plots
plot_grid(glx_subpops, thr_subpops, rel_widths = c(1,2), labels = NA)

# ggsave("manuscript_plots/violinplot_d15N_subpop.jpg", dpi = 300, width = 6, height = 5)
```

## Within-population variation:

d15N individuals with duplicates across years: 
```{r}
# Filter to include duplicates across years, but exclude duplicates within year: 
d15N_dups_across <- d15N_means %>% 
  filter(!duplicate_other_year == "0") %>% 
  filter(!duplicate_in_year == "2")
```

Plot values across years:
```{r}
# Set colors
duplicate_cols <- c("#0071b3", "#696fc6", "#ac64c1", "#df58a5", "#fd5c7a", "#ff7748", "#e69d00")

# Glx-Phe
ggplot(d15N_dups_across, aes(x = Year, y = Glx_Phe, group = duplicate_id, color = duplicate_id, label = DFO_sample_id)) + 
  geom_point() + 
  geom_line() + 
  geom_text_repel(hjust = -0.1, vjust = -0.1, cex = 3) +
  scale_x_continuous(breaks = seq(13, 2022, 1)) +
  scale_color_manual(values = duplicate_cols) + 
  xlab("Sampling Year") +
  ylab(expression(paste(delta^{15}, N["Glx-Phe"], " (\u2030)"))) +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16))

#ggsave("plots/d15N_dups_glx-phe.jpg", dpi = 300, width = 8, height = 4)

# Thr 
ggplot(d15N_dups_across, aes(x = Year, y = Thr, group = duplicate_id, color = duplicate_id, label = DFO_sample_id)) + 
  geom_point() + 
  geom_line() + 
  geom_text_repel(hjust = -0.1, vjust = -0.1, cex = 3) +
  scale_x_continuous(breaks = seq(13, 2022, 1)) +
  scale_color_manual(values = duplicate_cols) + 
  xlab("Sampling Year") +
  ylab(expression(paste(delta^{15}, N["Thr"], " (\u2030)"))) +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16))

#ggsave("plots/d15N_dups_thr.jpg", dpi = 300, width = 8, height = 4)

# Thr-Phe 
ggplot(d15N_dups_across, aes(x = Year, y = Thr_Phe, group = duplicate_id, color = duplicate_id, label = DFO_sample_id)) + 
  geom_point() + 
  geom_line() + 
  geom_text_repel(hjust = -0.1, vjust = -0.1, cex = 3) +
  scale_x_continuous(breaks = seq(13, 2022, 1)) +
  scale_color_manual(values = duplicate_cols) + 
  xlab("Sampling Year") +
  ylab(expression(paste(delta^{15}, N["Thr-Phe"], " (\u2030)"))) +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16))

#ggsave("plots/d15N_dups_thr-phe.jpg", dpi = 300, width = 8, height = 4)
```

Calculate differences between across year duplicates:
```{r}
# For Glx-Phe
d15N_duplicate_difference_Glx_Phe <- d15N_dups_across %>% 
  # group and arrangy by duplicate id - double checked that they are in the right year order 
  group_by(duplicate_id) %>% 
  arrange(.by_group = TRUE) %>% 
  # Add a column to show whether it was the first or second sample collected
  mutate(sample_order = 1:2) %>% 
  # Select columns for manipulation and pivot wider by duplicate ID, with first sample collected in col 1 and second sample collected in col 2
  dplyr::select(duplicate_id, sample_order, Glx_Phe) %>% 
  pivot_wider(names_from = sample_order, values_from = Glx_Phe) %>% 
  # rename columns 1 and 2: 
  dplyr::rename("sample1" = "1", "sample2" = "2") %>% 
  # Difference between sample values: 
  mutate(diff_Glx_Phe = sample2 - sample1)

# See table 
d15N_duplicate_difference_Glx_Phe

# Do the same for Thr: 
d15N_duplicate_difference_Thr <- d15N_dups_across %>% 
  group_by(duplicate_id) %>% 
  arrange(.by_group = TRUE) %>% 
  mutate(sample_order = 1:2) %>% 
  dplyr::select(duplicate_id, sample_order, Thr) %>% 
  pivot_wider(names_from = sample_order, values_from = Thr) %>% 
  dplyr::rename("sample1" = "1", "sample2" = "2") %>% 
  mutate(diff_Thr = sample2 - sample1)

d15N_duplicate_difference_Thr

# And for Thr-Phe: 
d15N_duplicate_difference_Thr_Phe <- d15N_dups_across %>% 
  group_by(duplicate_id) %>% 
  arrange(.by_group = TRUE) %>% 
  mutate(sample_order = 1:2) %>% 
  dplyr::select(duplicate_id, sample_order, Thr_Phe) %>% 
  pivot_wider(names_from = sample_order, values_from = Thr_Phe) %>% 
  dplyr::rename("sample1" = "1", "sample2" = "2") %>% 
  mutate(diff_Thr_Phe = sample2 - sample1)

d15N_duplicate_difference_Thr_Phe
```

Stats for individual inter-annual differences
```{r}
# Calculate min, max, and mean difference:
min(d15N_duplicate_difference_Glx_Phe$diff_Glx_Phe)
max(d15N_duplicate_difference_Glx_Phe$diff_Glx_Phe)
mean_diff_Glx_Phe = mean(d15N_duplicate_difference_Glx_Phe$diff_Glx_Phe)
mean_diff_Glx_Phe

min(d15N_duplicate_difference_Thr_Phe$diff_Thr_Phe)
max(d15N_duplicate_difference_Thr_Phe$diff_Thr_Phe)
mean_diff_Thr_Phe = mean(d15N_duplicate_difference_Thr_Phe$diff_Thr_Phe)
mean_diff_Thr_Phe

min(d15N_duplicate_difference_Thr$diff_Thr)
max(d15N_duplicate_difference_Thr$diff_Thr)
mean_diff_Thr     = mean(d15N_duplicate_difference_Thr$diff_Thr)
mean_diff_Thr

# Calculate mean difference of absolute values:
absmean_diff_Glx_Phe = mean(abs(d15N_duplicate_difference_Glx_Phe$diff_Glx_Phe))
absmean_diff_Glx_Phe
absmean_diff_Thr_Phe = mean(abs(d15N_duplicate_difference_Thr_Phe$diff_Thr_Phe))
absmean_diff_Thr_Phe
absmean_diff_Thr     = mean(abs(d15N_duplicate_difference_Thr$diff_Thr))
absmean_diff_Thr
```

## Potential confounding variables: 

Plot values by sampling date (in julian day):
```{r}
# Glx-Phe
julian_glx_phe <- ggplot(d15N_dups_removed, aes(x = julian_day, y = Glx_Phe)) + 
  geom_point() + 
  geom_smooth(method = lm, col = "#0072B2", fill = "#c6eaff") +
  labs(x = "", y = "", title = "Glx-Phe", size = 20) +
  theme_bw()

# Thr
julian_thr <- ggplot(d15N_dups_removed, aes(x = julian_day, y = Thr)) + 
  geom_point() + 
  geom_smooth(method = lm, col = "#0072B2", fill = "#c6eaff") +
  labs(x = "", y = "", title = "Thr", size = 20) +
  theme_bw()

# Thr-Phe
julian_thr_phe <- ggplot(d15N_dups_removed, aes(x = julian_day, y = Thr_Phe)) + 
  geom_point() + 
  geom_smooth(method = lm, col = "#0072B2", fill = "#c6eaff") +
  labs(x = "", y = "", title = "Thr-Phe", size = 20) +
  theme_bw()

# Arrange plots:
plot_grid(julian_glx_phe, julian_thr, julian_thr_phe, ncol = 1) + 
  draw_label("Day of Year", x = 0.5, y = 0, vjust = -0.3, size = 14) + 
  draw_label(expression(paste(delta^{15}, "N", " (\u2030)")), 
             x = 0, y = 0.5, vjust = 1.1, angle = 90, size = 14)

# ggsave("manuscript_plots/d15N_x_julianDay.jpg", dpi = 300, width = 5, height = 6)
```

Test whether Glx-Phe, Thr, and Thr-Phe differ with sampling date:

Glx-Phe: 
```{r}
# # Model (run on server)
# Glx_Phe__julian_day <- brm(Glx_Phe ~ genetic_pop + julian_day,
#                            data = d15N_dups_removed,
#                            warmup = 20000,
#                            iter = 50000,
#                            chains = 3,
#                            init = "random",
#                            cores = 2)
# 
# # Save model (server):
# saveRDS(Glx_Phe__julian_day, "output/Glx_Phe__julian_day.rds")

# Load model and view results
Glx_Phe__julian_day <- readRDS("server/Glx_Phe__julian_day.rds")
summary(Glx_Phe__julian_day)
```

Thr: 
```{r}
# # Model (run on server)
# Thr__julian_day <- brm(Thr ~ genetic_pop + julian_day,
#                            data = d15N_dups_removed,
#                            warmup = 20000,
#                            iter = 50000,
#                            chains = 3,
#                            init = "random",
#                            cores = 2)
# 
# # Save model (server):
# saveRDS(Thr__julian_day, "output/Thr__julian_day.rds")

# Load model and view results
Thr__julian_day <- readRDS("server/Thr__julian_day.rds")
summary(Thr__julian_day)
```

Thr-Phe
```{r}
# # Model (run on server)
# Thr_Phe__julian_day <- brm(Thr_Phe ~ genetic_pop + julian_day,
#                            data = d15N_dups_removed,
#                            warmup = 20000,
#                            iter = 50000,
#                            chains = 3,
#                            init = "random",
#                            cores = 2)
# 
# # Save model (server):
# saveRDS(Thr_Phe__julian_day, "output/Thr_Phe__julian_day.rds")

# Load model and view results
Thr_Phe__julian_day <- readRDS("server/Thr_Phe__julian_day.rds")
summary(Thr_Phe__julian_day)
```

No relationship with Julian day for Glx-Phe, Thr, and Thr-Phe.

What about differences between sexes?
```{r}
fill_cols_sex <- c("#ff8b8b", "#8bc5ff")
outline_cols_sex <- c("#8b0000", "#00468b")

# Arrange data for Phe, Lys, and Glx-Phe
d15N_means_rearrange_glx <- d15N_means_rearrange %>% 
  dplyr::filter(name %in% c("Glx_Phe")) 

# Arrange data for Thr and Thr-Phe
d15N_means_rearrange_thr <- d15N_means_rearrange %>% 
  dplyr::filter(name %in% c("Thr", "Thr_Phe")) 

# Plot Phe, Lys, and Glx-Phe
glx_sex <- ggplot(data = d15N_means_rearrange_glx, aes(x = name, y = value, fill = sex, colour = sex)) + 
  geom_violin(position = position_dodge(0.75)) + 
  geom_boxplot(width = 0.075, position = position_dodge(0.75), fill = "white") +
  geom_point(position = position_jitterdodge(jitter.width = 0.2), size = 0.3, alpha = 0.6) +  
  ylim(0,40) +
  ylab(expression(paste(delta^{15}, "N", " (\u2030)"))) +
  scale_fill_manual(values = fill_cols_sex, name = "Sex", labels = c("Female", "Male")) + 
  scale_colour_manual(values = outline_cols_sex, name = "Sex", labels = c("Female", "Male")) +
  scale_x_discrete(labels = c("Glx_Phe" = "Glx-Phe")) +
  theme_classic() + 
  theme(legend.position = "none",
        legend.background = element_blank(),
        axis.text = element_text(size = 16, colour = "black"),
        axis.title = element_text(size = 18),
        axis.title.x = element_blank())

# Plot Thr and Thr-Phe
thr_sex <- ggplot(data = d15N_means_rearrange_thr, aes(x = name, y = value, fill = sex, colour = sex)) + 
  geom_violin(position = position_dodge(0.75)) + 
  geom_boxplot(width = 0.075, position = position_dodge(0.75), fill = "white") +
  geom_point(position = position_jitterdodge(jitter.width = 0.2), size = 0.3, alpha = 0.6) +  
  ylim(-70,-30) +
  scale_fill_manual(values = fill_cols_sex) + 
  scale_colour_manual(values = outline_cols_sex) +
  scale_x_discrete(labels = c("Thr" = "Thr", "Thr_Phe" = "Thr-Phe")) +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 16, colour = "black"))

# Combine plots
plot_grid(glx_sex, thr_sex, rel_widths = c(1.2,1.8), labels = NA)

# ggsave("manuscript_plots/violinplots_d15N_sex.jpg", dpi = 300, width = 6, height = 5)
```

Test whether Glx-Phe, Thr, and Thr-Phe differ between sexes:

Glx-Phe: 
```{r}
# # Model (run on server)
# Glx_Phe__sex <- brm(Glx_Phe ~ genetic_pop + sex,
#                     data = d15N_dups_removed,
#                     warmup = 20000,
#                     iter = 50000,
#                     chains = 3,
#                     init = "random",
#                     cores = 2)
# 
# # Save model (server):
# saveRDS(Glx_Phe__sex, "output/Glx_Phe__sex.rds")

# Load model and view results
Glx_Phe__sex <- readRDS("server/Glx_Phe__sex.rds")
summary(Glx_Phe__sex)
```

Thr:
```{r}
# # Model (run on server)
# Thr__sex <- brm(Thr ~ genetic_pop + sex,
#                 data = d15N_dups_removed,
#                 warmup = 20000,
#                 iter = 50000,
#                 chains = 3,
#                 init = "random",
#                 cores = 2)
# 
# # Save model (server):
# saveRDS(Thr__sex, "output/Thr__sex.rds")

# Load model and view results
Thr__sex <- readRDS("server/Thr__sex.rds")
summary(Thr__sex)
```

Thr-Phe:
```{r}
# # Model (run on server)
# Thr_Phe__sex <- brm(Thr_Phe ~ genetic_pop + sex,
#                     data = d15N_dups_removed,
#                     warmup = 20000,
#                     iter = 50000,
#                     chains = 3,
#                     init = "random",
#                     cores = 2)
# 
# # Save model (server):
# saveRDS(Thr_Phe__sex, "output/Thr_Phe__sex.rds")

# Load model and view results
Thr_Phe__sex <- readRDS("server/Thr_Phe__sex.rds")
summary(Thr_Phe__sex)
```

No difference between sexes for Glx-Phe, Thr, and Thr-Phe.

## Diagnostics & Posterior Predictive Checks

Model to be checked: 
```{r}
# model to evaluate 
model <- Thr__genetic_pop   
# model name
model_name <- "Thr__genetic_pop"
# Glx_Phe, Thr, or Thr_Phe
values <- "Thr"               
# genetic_pop
group <- "genetic_pop"            
```

Set color scheme: 
```{r}
# diag_cols <- c("#004064", "#00659e", "#008bd9", "#15abff", "#d9f1ff", "#edf8ff")
```

Change default font size: 
```{r}
bayesplot_theme_update(text = element_text(size = 12))
```

Check Gelman-Rubin Diagnostics: 
```{r}
gr_diag <- brms::rhat(model)
#write.csv(gr_diag, file = paste("output/gelmanrubin_", model_name, ".csv", sep=""))
```

Traceplot and posterior density: 
```{r}
# Rename parameters: 
model_array <- as.array(model)
dimnames(model_array)[[3]] <- c("Intercept", "ECAG2", "Sigma", "Intercept", "lprior", "lp__")

# Set pars for plots:
pars = c("Intercept", "ECAG2", "Sigma")

# Traceplots: 
traceplot <- mcmc_trace(model_array, pars = pars, facet_args = list(ncol = 1, strip.position = "left"))
# ggsave(traceplot, filename = paste("manuscript_plots/posterior_plots/", model_name, "__traceplot.jpeg"), units="in", width = 5.5, height = 3.5, dpi = 300)

# Density plots: 
dens_plot <- mcmc_dens_overlay(model_array, pars = pars)
# ggsave(dens_plot, filename = paste("manuscript_plots/posterior_plots/", model_name, "__densplot.jpeg"), units="in", width = 8.5, height = 2.5, dpi = 300)
```

Autocorrelation plot: 
```{r}
mcmc_acf(model_array, pars = pars)
#ggsave(paste("plots/", model_name, "__autocorrplot.jpeg"), dpi = 300, width = 8, height = 5)
```

Change default font size for next set of plots: 
```{r}
bayesplot_theme_update(text = element_text(size = 18))
```

Check model fit with posterior predictive check: 
```{r}
#Kernel density or empirical CDF estimates of each dataset (row) in yrep are overlaid, with the distribution of y itself on top (and in a darker shade). When using ppc_ecdf_overlay() with discrete data, set the discrete argument to TRUE for better results.
pp_check_dens_overlay <- pp_check(model, 
         type = "dens_overlay_grouped", 
         ndraws = 100, 
         group = group)

pp_check_dens_overlay + 
  #scale_x_continuous(limits = c(-70, -40), breaks = seq(-65, -40, by = 5)) +  
  theme(legend.text = element_text(size = 18),
        axis.text.x = element_text(size = 18))

# ggsave(paste("manuscript_plots/posterior_plots/", model_name, "__ppcheck_densoverlay.jpeg"), dpi = 300, width = 8, height = 5)

pp_check(model, 
         type = "stat_grouped", 
         stat = "mean",
         ndraws = 100, 
         group = group)

#ggsave(paste("plots/", model_name, "__ppcheck_meangrouped.jpeg"), dpi = 300, width = 8, height = 5)

# A scatterplot showing the joint distribution of two statistics computed over the datasets (rows) in yrep. The value of the statistics in the observed data is overlaid as large point.
pp_check(model, 
         type = "stat_2d", 
         stat = c("mean", "sd"))

#ggsave(paste("plots/", model_name, "__ppcheck_stat2d.jpeg"), dpi = 300, width = 8, height = 5)
```

Visualize the d15N values per group with associated uncertainty:
```{r}
model %>%
  # spread 1000 posterior samples for 2 parameters in wide format
  spread_draws(b_Intercept, b_genetic_groupECAG2, ndraws = 1000, seed = 123) %>%
  # calculate average numbers and convert to long format for visualisation
  mutate(ECAG1 = b_Intercept,
         ECAG2 = b_Intercept + b_genetic_groupECAG2) %>%
  pivot_longer(cols = c("ECAG1", "ECAG2"), 
               names_to = group,                
               values_to = values) %>%
  # visualise via ggplot()
  ggplot(aes(y = Thr_Phe, x = genetic_pop, color = genetic_pop, fill = genetic_pop)) +
    stat_eye(point_interval = "median_qi", .width = c(0.6, 0.9)) + 
    scale_color_manual(values = outline_cols) +
    scale_fill_manual(values = fill_cols) +
    ylab(expression(paste(delta^{15}, N["Thr-Phe"], " (\u2030)"))) +
    theme_classic() + 
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.text.x = element_text(size = 18),
          axis.title.y = element_text(size = 18),
          axis.text.y = element_text(size = 16))

# ggsave(paste("manuscript_plots/posterior_plots/", model_name, "__spreaddraws.jpeg"), dpi = 300, width = 7, height = 5)
```





